On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-04-26 manuscript/manuscript.tex
responded to comments

The invalidity of the standard statistic for serially dependent data can be
illustrated by a simple simulation study. Consider a first-order autoregressive
or AR(1) model with marginal normal (or gamma) distribution. For each AR
coefficient $\psi \in \{-0.3, -0.1, 0.1, 0.3\}$, we generated 1000
series of length 200. For each series, we applied the KS statistic
in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(8, 8)$ (or 
$\Gamma(8,1)$) marginally. The PP-plots of the p-values from $1000$ replicates 
for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. As 
$\phi$ diverges from 0, the p-values look less likely to be generated from a 
standard uniform distributions. Positive $\psi$ values led to p-values with a 
distribution function higher than the standard uniform distribution function and, 
hence, conservative tests. Negative $\psi$ values led to p-values with a 
distribution function lower than the standard uniform distribution and, hence, 
liberal tests. \eds{the previous two sentences are not consistent with what is 
written at the beginning of this section. If I am interpreting the plots 
correctly, then positive $\psi$ leads to p-values that are too low which would
correspond to liberal tests (consistent with what was written at the beginning 
of this section).}

@@

@@

In particular, let
$Z_i = \Phi^{-1}\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
function of the standard normal. Then we fit an ARMA$(p, q)$ model to
$Z_1, \ldots, Z_n$ with AR order $p$ and MA order $q$ selected by the Akaike
Information Criterion (AIC). This can be done with, for example, function
\texttt{auto.arima()} from  R package \texttt{forecast}
\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s is
zero, it is necessary to set the intercept of the ARMA model as zero in the
fitting process. This restriction turned out to be critical in our
investigation; having the intercept estimated does not lead to desired p-value
distributions in the following bootstrap process.
The selected ARMA$(p, q)$ model with fitted
parameters will be used as the working model to generate bootstrap samples with
serial dependence mimicking that in the observed data. The unconditional
variance $\sigma^2$ of the ARMA model with unit innovation variance can be
obtained with function
\texttt{tacvfARMA()} from R package \texttt{ltsa} \citep{mcleod2007algorithms}.

@@

The semiparametric bootstrap procedure was evaluated in simulation. We 
considered three true dependence structures on the standard normal scale 
(ARMA(1, 1), AR(2), and MA(1)) and two marginal distributions 
($N(8,8)$ and $\Gamma(8,1)$).  For each dependence structure and marginal distribution combination, we generated 1000 series of length 200.  For each series, we applied the semiparametric bootstrap procedure with serial
dependence accounted for through a working ARMA model to test $H_0$ that the 
$X_i$'s marginally follow their true marginal distribution ($N(8, 8)$ or 
$\Gamma(8,1)$). Figure~\ref{fig:pp_ss} displays the PP-plots of the 1000 
p-values for each dependence structure and marginal distribution combination.
All plots within the figure show the points falling along the diagonal lines, 
implying that the p-values are coming from standard uniform distributions and 
that the semiparametric bootstrap procedure is an effective remedy in all cases
considered.

@@

@@

Figure~\ref{fig:pp_ssf} shows the results of the
procedure performed on data generated with dependence structures of ARMA(1, 1),
AR(2), and MA(1). Naively fitting parameters and not adjusting for dependence  clearly deviates from a uniform distribution of p-values. 
Parametric bootstrap provides some correction but does not account for 
dependence, 
\eds{just want to verify: you are using parametric bootstrap from Section 2 for
the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
that ignores both issues)} 
so therefore the results of the copula remedy are more accurate and favorable.
%In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
%to our assumption of AR(1) that the results are reasonable. AR(2) however
%appears to be just far enough from our assumption, showing a limitation of the
%procedure.

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an ARMA$(p,q)$
dependence structure. As long as this assumption is a close approximation, the
correction should still provide a reasonable approximation that can be useful 
for practical purposes. 
%Regardless of the true dependence in the data we assume an AR(1)
%dependence structure by taking the lag-1 sample auto-spearman rho. However, we
%can show that as long as the AR(1) assumption is a close approximation, the
%correction still provides a reasonable approximation that can be useful for
%practical purposes.

\begin{table}[ht]
  \label{tab:power}
  \caption{Power of rejecting the null hypothesis of normal and gamma
    distribution at significance level 0.05 when the true distribution was
    $\Gamma(8, 1)$ and $N(8, 8)$, respectively. }
\centering
\begin{tabular}{llrrrr}
  \toprule
  &  & \multicolumn{2}{c}{$H_0:$ normal} &
  \multicolumn{2}{c}{$H_0$: gamma}\\
  \cmidrule(lr){3-4}\cmidrule(lr){5-6}
  Dependence & Method & $n = 100$ & $n = 200$ & $n = 100$ & $n = 200$\\
  \midrule
ARMA & naive & 0.40 & 0.66 & 0.52 & 0.78 \\ 
   & copula & 0.33 & 0.56 & 0.44 & 0.72 \\ 
  AR & naive & 0.41 & 0.66 & 0.46 & 0.70 \\ 
   & copula & 0.26 & 0.45 & 0.31 & 0.54 \\ 
  MA & naive & 0.37 & 0.73 & 0.51 & 0.82 \\ 
   & copula & 0.34 & 0.69 & 0.49 & 0.80 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{babu2004goodness}. In the case of serially dependent data, 
a procedure using bootstrap with copulas to model dependency shows positive
results. When both assumptions are violated, i.e., where the data has serial 
dependence and parameters must be fitted, an adjusted copula procedure also 
shows positive results. The tests appear effective for a variety of families of 
distributions. The copula remedy is not a complete solution and has limitations. 
Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
%Therefore, if the AR(1) dependence structure is a 
%close approximation of the truth, the approach can work.
%However, in cases such as AR(2), if 
%the approximation is too far from the true
%dependence structure the approach does not completely remedy the issue.
Therefore, if the assumed dependence structure is a close approximation of the
truth, the approach can work. However, if the approximation is too far from the 
true dependence structure the approach does not completely remedy the issue. 
As well, tests were only performed with the normal copula. It is possible that 
other copulas could provide stronger results based on the true dependence of the 
data.

>>>>

\jy{how about removing the panels for $-0.1$ and 0.1?}

@@

The invalidity of the standard statistic for serially dependent data can be
illustrated by a simple simulation study. Consider a first-order autoregressive
or AR(1) model with marginal normal (or gamma) distribution. For each AR
coefficient $\psi \in \{-0.3, -0.1, 0.1, 0.3\}$, we generated 1000
series of length 200. For each series, we applied the KS statistic
in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(8, 8)$ (or 
$\Gamma(8,1)$) marginally. The PP-plots of the p-values from $1000$ replicates 
for all the $\psi$ values are displayed in Figure~\ref{fig:pp_s}. As 
$\phi$ diverges from 0, the p-values look less likely to be generated from a 
standard uniform distributions. Positive $\psi$ values led to p-values with a 
distribution function higher than the standard uniform distribution function and, 
hence, conservative tests. Negative $\psi$ values led to p-values with a 
distribution function lower than the standard uniform distribution and, hence, 
liberal tests. \eds{the previous two sentences are not consistent with what is 
written at the beginning of this section. If I am interpreting the plots 
correctly, then positive $\psi$ leads to p-values that are too low which would
correspond to liberal tests (consistent with what was written at the beginning 
of this section).} \jy{Need to rephrase. A distribution function higher than
  another distribution means that it has more smaller values.}

@@

In particular, let
$Z_i = \Phi^{-1}\{ F(X_i)\}$, $i = 1, \ldots, n$, where $\Phi$ is the distribution
function of the standard normal. Then we fit an ARMA$(p, q)$ model to
$Z_1, \ldots, Z_n$ with AR order $p$ and MA order $q$ selected by the Akaike
Information Criterion (AIC). This can be done with, for example, function
\texttt{auto.arima()} from  R package \texttt{forecast}
\citep{hyndman2008automatic}. Since it is known that the mean of $Z_i$'s is
zero, it is necessary to set the intercept of the ARMA model as zero in the
fitting process. This restriction turned out to be critical from our
investigation; having the intercept estimated does not lead to desired p-value
distributions in the following bootstrap process.
The selected ARMA$(p, q)$ model with fitted
parameters will be used as the working model to generate bootstrap samples with
serial dependence mimicking that in the observed data. The unconditional
variance $\sigma^2$ of the ARMA model with unit innovation variance can be
obtained with function
\texttt{tacvfARMA()} from R package \texttt{ltsa} \citep{mcleod2007algorithms}.

@@

@@

The semiparametric bootstrap procedure was evaluated in a simulation study. We
considered two marginal distributions: $N(8,8)$ and $\Gamma(8,1)$. Three
dependence structures were used to link variables generated from each marginal
distribution; on the standard normal scale, they are
ARMA(1, 1) with AR coefficient 0.5 and MA coefficient 0.3;
AR(2) with coefficients $(0.6, 0.2)$; and
MA(1)) with coefficient 0.8.
For each dependence structure and marginal distribution combination, we
generated 1000 series of length 200.  For each series, we applied the
semiparametric bootstrap procedure with serial
dependence accounted for through a working ARMA model to test $H_0$ that the 
$X_i$'s marginally follow their true marginal distribution ($N(8, 8)$ or 
$\Gamma(8,1)$). Figure~\ref{fig:pp_ss} displays the PP-plots of the 1000 
p-values for each dependence structure and marginal distribution combination.
All plots within the figure show the points falling along the diagonal lines, 
implying that the p-values are coming from standard uniform distributions and 
that the semiparametric bootstrap procedure is an effective remedy in all cases
considered.

@@

Figure~\ref{fig:pp_ssf} shows the PP-plots resulting p-valuess of the
procedure performed on data generated from same simulation settings as in
Section~\ref{sec:dependence}. For comparison, we also displayed the PP-plot of
a naive bootstrap procedure that adjusts for the unspecified parameters as in
Section~\ref{sec:fitted} but not for the serial dependence. The p-values from
naively fitting parameters but not adjusting for dependence clearly deviates
from the standard uniform distribution except in the MA(1) case.
\jy{needs an explanation ...}
The super naive approach that does not adjust for fitted parameters nor serial
dependence would have double sin, so the results are not reported.
\eds{just want to verify: you are using parametric bootstrap from Section 2 for
the top portion of Figure~\ref{fig:pp_ssf}? (Not the totally naive procedure 
that ignores both issues)} \jy{Yes}
Similar to Section~\ref{sec:dependence}, the working normal copula approach
gives p-values with the desired standard uniform distribution regardless of the
true dependence.

\begin{table}[tbp]
  \label{tab:power}
  \caption{Power of rejecting the null hypothesis of normal and gamma
    distribution at significance level 0.05 when the true distribution was
    $\Gamma(8, 1)$ and $N(8, 8)$, respectively. }
\centering
\begin{tabular}{llrrrr}
  \toprule
  &  & \multicolumn{2}{c}{$H_0:$ normal} &
  \multicolumn{2}{c}{$H_0$: gamma}\\
  \cmidrule(lr){3-4}\cmidrule(lr){5-6}
  Dependence & Method & $n = 100$ & $n = 200$ & $n = 100$ & $n = 200$\\
  \midrule
ARMA & naive & 0.40 & 0.66 & 0.52 & 0.78 \\ 
   & copula & 0.33 & 0.56 & 0.44 & 0.72 \\ 
  AR & naive & 0.41 & 0.66 & 0.46 & 0.70 \\ 
   & copula & 0.26 & 0.45 & 0.31 & 0.54 \\ 
  MA & naive & 0.37 & 0.73 & 0.51 & 0.82 \\ 
   & copula & 0.34 & 0.69 & 0.49 & 0.80 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{babu2004goodness}. In the case of serially dependent data, 
a procedure using bootstrap with copulas to model dependency shows positive
results. When both assumptions are violated, i.e., where the data has serial 
dependence and parameters must be fitted, an adjusted copula procedure also 
shows positive results. The tests appear effective for a variety of families of 
distributions. The copula remedy is not a complete solution and has limitations. 
Regardless of the true dependence, we assume an ARMA($p,q$) dependence structure. 
Therefore, if the assumed dependence structure is a close approximation of the
truth, the approach can work. However, if the approximation is too far from the 
true dependence structure the approach does not completely remedy the issue. 
As well, tests were only performed with the normal copula. It is possible that 
other copulas could provide stronger results based on the true dependence of the 
data.
